Pottery decor as networks on the Middle Niger

### 2024-05-29 analysis/paper/paper.Rmd
changes accroding to paper revisions

#plot
ggraph(early_flat_bb, layout = "stress") +
  geom_node_point() +
  geom_edge_fan(color = "grey", alpha = 0.8) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph()
```

>>>>

# put cumulative edge weights back into the backbone
flat_edges <- early_flat |> 
  get.data.frame("edges")

early_flat_bb <- early_flat_bb |> 
  activate(edges) |> 
  select(-weight) |> 
  left_join(flat_edges)

#plot
ggraph(early_flat_bb, layout = "stress") +
  geom_node_point(aes(size = centrality_betweenness())) +
  geom_edge_fan(aes(width = weight), color = "grey", alpha = 0.8) +
  scale_edge_width(range = c(0.2, 3)) +
  geom_node_text(aes(label = label), repel = TRUE) +
  theme_graph()
```
